Throughput Prediction on 60 GHz Devices for Latency Sensitive Applications

### 2021-01-21 paper.tex
changes

% mmWave
\cite{wei:mobicom2017,zhou:infocom2018} are a couple of the works which utlize 60 GHz wireless to enable applications such as VR, AR, and Miracast.~\cite{wei:mobicom2017} proposes the idea of having multiple APs and as the client device moves, it can keep switching to a different AP that works best for that position. This work showed that as the client moves out of the AP's FoV, the client's performance drops drastically and often loses connectivity. We also have a similar finding in this work. However, they did not look at the time-varying nature of throughput that we observed even when the phone is within the AP's FoV.~\cite{zhou:infocom2018} found that typical VR/Miracast motion can be rather unpredictable and hence lead to large and sudden drops in signal quality. Thus, they did not try to predict the throughput and instead devised a way to reduce the search space for 60 GHz beamforming.
%In terms of mmWave

>>>>

% mmWave
\cite{wei:mobicom2017,zhou:infocom2018} 
utlize 60 GHz wireless to enable applications such as VR, AR,
and Miracast.
\cite{wei:mobicom2017} proposes the idea of having
multiple APs and as the client device moves, it can keep switching to
a different AP that works best for that position. This work showed
that as the client moves out of the AP's FoV, the client's performance
drops drastically and often loses connectivity. Our work has a similar
finding. However, their work did not look at the time-varying
nature of throughput that we observed even when the phone is within
the AP's FoV.
\cite{zhou:infocom2018} found that typical VR/Miracast
motion can be rather unpredictable and hence lead to large and sudden
drops in signal quality. They did not try to predict the
throughput but instead devised a way to reduce the search space for 60
GHz beamforming.
%In terms of mmWave
